P versus NP

### 2020-02-25 doc/manuscript.tex
Fixed bug

\begin{proof}
Since every problem in $L$ is $\textit{L--complete}$ under logarithmic space reduction, then we can interpret the quantification of the above statement as $``$For any language $L_{1}$ in $L$, there is an $\textit{NP--complete}$ language $L_{2}$ $\ldots$ (rest is the same)$"$. However, if we can choose an arbitrary language $L_{1}$ in $L$, then choosing $L_{1}$ the trivial language $\{1\}$ will result in the right hand side of the expression defining $L_{2}$ contained in $NL$. Moreover, if that problem in $NL$ is $\textit{NP--complete}$ under logarithmic space reduction, then we obtain that certainly $NL = NP$.
\end{proof}

>>>>

\begin{proof}
Since every problem in $L$ is $\textit{L--complete}$ under logarithmic space reduction, then we can interpret the quantification of the above statement as $``$For any nonempty language $L_{1}$ in $L$, there is an $\textit{NP--complete}$ language $L_{2}$ $\ldots$ (rest is the same)$"$. However, if we can choose an arbitrary language $L_{1}$ in $L$, then choosing $L_{1}$ the trivial language $\{1\}$ will result in the right hand side of the expression defining $L_{2}$ contained in $NL$. Moreover, if that problem in $NL$ is $\textit{NP--complete}$ under logarithmic space reduction, then we obtain that certainly $NL = NP$.
\end{proof}
